### 2022-02-14 src/text/2-package-subsections/modeling.tex
adapt reference to agnpy

The model gallery provides a visual overview of the available models in Gammapy.
Most of the analytic models  commonly used in gamma-ray astronomy are built-in. We also offer a wrapper to radiative models implemented in the Naima package \cite{naima}. The modeling framework can be easily extended with user-defined models. For example agnpy \citep{cosimo_nigro_2021_5762147} models that describe leptonic radiative processes in jetted Active Galactic Nuclei (AGN) can wrapped into gammapy \footnote{as shown in the following tutorial \url{ https://agnpy.readthedocs.io/en/latest/tutorials/ec_dt_gammapy_fit.html}}.

>>>>

The model gallery provides a visual overview of the available models in Gammapy.
Most of the analytic models  commonly used in gamma-ray astronomy are built-in. We also offer a wrapper to radiative models implemented in the Naima package \cite{naima}. The modeling framework can be easily extended with user-defined models. For example agnpy models that describe leptonic radiative processes in jetted Active Galactic Nuclei (AGN) can wrapped into gammapy \citep[see section3.5 of ][]{2021arXiv211214573N} .
